\bf Range Analysis for the IonMonkey JavaScript engine

### 2012-05-02 project-writings/paper.tex
aesthetics of tables

\hline\hspace{1em} cube:              & ??               &  25.1ms $\pm$ 0.3\% &   25.2ms $\pm$ 0.4\%   &  \textit{might} be 1.001x as slow \\
\hline\hspace{1em} morph:             & ??               &   6.9ms $\pm$ 0.5\% &    6.9ms $\pm$ 0.4\%   &  \textit{might} be 1.003x as slow \\
\hline\hspace{1em} raytrace:          & 1.009x as slow &  20.4ms $\pm$ 0.5\% &   20.6ms $\pm$ 0.4\%   &  significant \\

@@

\hline\hspace{1em} binary-trees:      & 1.019x as slow &   3.0ms $\pm$ 0.9\% &    3.0ms $\pm$ 0.9\%   &  significant \\
\hline\hspace{1em} fannkuch:          & 1.034x as fast   &   8.8ms $\pm$ 0.3\% &    8.5ms $\pm$ 0.4\%   &  significant \\
\hline\hspace{1em} nbody:             & 1.035x as fast   &   3.6ms $\pm$ 0.6\% &    3.5ms $\pm$ 0.3\%   &  significant \\
\hline\hspace{1em} nsieve:            & 1.052x as slow &   3.1ms $\pm$ 0.6\% &    3.3ms $\pm$ 0.5\%   &  significant \\

@@

\hline\hspace{1em} 3bit-bits-in-byte: & 1.009x as fast   &   1.0ms $\pm$ 0.6\% &    1.0ms $\pm$ 0.6\%   &  significant \\
\hline\hspace{1em} bits-in-byte:      & 1.023x as fast   &   4.1ms $\pm$ 0.5\% &    4.0ms $\pm$ 0.6\%   &  significant \\
\hline\hspace{1em} bitwise-and:       & ??               &   2.8ms $\pm$ 0.5\% &    2.8ms $\pm$ 0.6\%   &  \textit{might} be 1.005x as slow \\
\hline\hspace{1em} nsieve-bits:       & -                &   3.6ms $\pm$ 0.5\% &    3.6ms $\pm$ 0.5\% & \\

@@

\hline\hspace{1em} recursive:         & 1.020x as slow &   2.3ms $\pm$ 0.7\% &    2.3ms $\pm$ 0.4\%   &  significant \\

@@

\hline\hspace{1em} aes:               & 1.009x as slow &  15.5ms $\pm$ 0.4\% &   15.6ms $\pm$ 0.4\%   &  significant \\
\hline\hspace{1em} md5:               & ??               &   6.9ms $\pm$ 0.7\% &    6.9ms $\pm$ 0.4\%   &  \textit{might} be 1.006x as slow \\
\hline\hspace{1em} sha1:              & 1.008x as slow &   4.9ms $\pm$ 0.5\% &    4.9ms $\pm$ 0.5\%   &  significant \\

@@

\hline\hspace{1em} format-tofte:      & -                &  42.6ms $\pm$ 0.2\% &   42.6ms $\pm$ 0.2\%   & \\
\hline\hspace{1em} format-xparb:      & 1.023x as fast   &  20.0ms $\pm$ 0.3\% &   19.5ms $\pm$ 0.3\%   &  significant \\

@@

\hline\hspace{1em} cordic:            & 1.021x as fast   &   2.7ms $\pm$ 0.4\% &    2.6ms $\pm$ 0.6\%   &  significant \\
\hline\hspace{1em} partial-sums:      & -                &   7.1ms $\pm$ 0.5\% &    7.1ms $\pm$ 0.6\% & \\
\hline\hspace{1em} spectral-norm:     & 1.024x as slow &   3.4ms $\pm$ 0.6\% &    3.5ms $\pm$ 0.4\%   &  significant \\

@@

\hline\hspace{1em} dna:               & 1.012x as fast   &  10.2ms $\pm$ 0.5\% &   10.0ms $\pm$ 0.4\%   &  significant \\

@@

\hline\hspace{1em} base64:            & ??               &   4.9ms $\pm$ 0.6\% &    4.9ms $\pm$ 0.4\%   &  \textit{might} be 1.006x as slow \\
\hline\hspace{1em} fasta:             & 1.012x as slow &   6.9ms $\pm$ 0.5\% &    6.9ms $\pm$ 0.4\%   &  significant \\
\hline\hspace{1em} tagcloud:          & -                &  23.2ms $\pm$ 0.4\% &   23.3ms $\pm$ 0.3\% & \\
\hline\hspace{1em} unpack-code:       & 1.014x as slow &  39.5ms $\pm$ 0.2\% &   40.1ms $\pm$ 0.3\%   &  significant \\
\hline\hspace{1em} validate-input:    & 1.007x as slow &   6.8ms $\pm$ 0.4\% &    6.9ms $\pm$ 0.5\%   &  significant  \\

@@

\begin{figure}[H]
\begin{tabular}{|l|l|l|l|l|}
\hline
    \textbf{Test}     &\textbf{Comparison} & \textbf{From}        & \textbf{To}           &  \textbf{Details} \\
\hline\hline
    Total:                      & 1.015x as fast   & 2319.6ms $\pm$ 0.3\% &  2285.4ms $\pm$ 0.4\%  &   significant\\
\hline\hline
      ai:                       & 1.118x as fast   &  121.3ms $\pm$ 0.8\% &   108.5ms $\pm$ 1.2\%  &   significant\\
\hline\hspace{1em} astar:                  & 1.118x as fast   &  121.3ms $\pm$ 0.8\% &   108.5ms $\pm$ 1.2\%  &   significant\\
\hline\hline
      audio:                    & -                &  842.8ms $\pm$ 0.4\% &   838.0ms $\pm$ 0.7\%  &\\
\hline\hspace{1em} beat-detection:         & ??               &  393.0ms $\pm$ 1.0\% &   397.6ms $\pm$ 1.5\%  &   \textit{might} be 1.012x as slow\\
\hline\hspace{1em} dft:                    & 1.030x as fast   &  162.6ms $\pm$ 0.6\% &   157.8ms $\pm$ 0.5\%  &   significant\\
\hline\hspace{1em} fft:                    & 1.016x as fast   &  123.5ms $\pm$ 0.2\% &   121.6ms $\pm$ 0.4\%  &   significant\\
\hline\hspace{1em} oscillator:             & 1.017x as fast   &  163.7ms $\pm$ 0.3\% &   160.9ms $\pm$ 0.3\%  &   significant\\
\hline\hline
      imaging:                  & 1.020x as fast   &  569.1ms $\pm$ 0.9\% &   557.9ms $\pm$ 1.3\%  &   significant\\
\hline\hspace{1em} gaussian-blur:          & -                &  197.2ms $\pm$ 1.7\% &   193.7ms $\pm$ 2.1\%  &\\
\hline\hspace{1em} darkroom:               & -                &  248.2ms $\pm$ 0.3\% &   247.6ms $\pm$ 0.4\%  &\\
\hline\hspace{1em} desaturate:             & 1.062x as fast   &  123.8ms $\pm$ 3.2\% &   116.7ms $\pm$ 5.1\%  &   significant\\
\hline\hline
      json:                     & 1.019x as fast   &  121.3ms $\pm$ 0.2\% &   119.0ms $\pm$ 0.4\%  &   significant\\
\hline\hspace{1em} parse-financial:        & 1.005x as fast   &   75.8ms $\pm$ 0.2\% &    75.5ms $\pm$ 0.4\%  &   significant\\
\hline\hspace{1em} stringify-tinderbox:    & 1.044x as fast   &   45.5ms $\pm$ 0.5\% &    43.5ms $\pm$ 0.8\%  &   significant\\
\hline\hline
      stanford:                 & -                &  665.0ms $\pm$ 0.5\% &   662.2ms $\pm$ 0.4\%  &\\
\hline\hspace{1em} crypto-aes:             & -                &  160.7ms $\pm$ 1.5\% &   160.6ms $\pm$ 1.1\%  &\\
\hline\hspace{1em} crypto-ccm:             & 1.008x as slow &  158.6ms $\pm$ 0.4\% &   159.8ms $\pm$ 0.5\%  &   significant\\
\hline\hspace{1em} crypto-pbkdf2:          & 1.006x as fast   &  254.9ms $\pm$ 0.5\% &   253.3ms $\pm$ 0.4\%  &   significant\\
\hline\hspace{1em} crypto-sha256-iterative:& 1.025x as fast   &   90.8ms $\pm$ 0.4\% &    88.5ms $\pm$ 0.5\%  &   significant \\
\hline
\end{tabular}
\caption{Kraken benchmark results}
\label{fig:kraken}
\end{figure}

>>>>

\hline\hspace{0.5em} cube:              & ??               &  25.1ms $\pm$ 0.3\% &   25.2ms $\pm$ 0.4\%   &  \textit{might} be 1.001x as slow \\
\hline\hspace{0.5em} morph:             & ??               &   6.9ms $\pm$ 0.5\% &    6.9ms $\pm$ 0.4\%   &  \textit{might} be 1.003x as slow \\
\hline\hspace{0.5em} raytrace:          & 1.009x as slow &  20.4ms $\pm$ 0.5\% &   20.6ms $\pm$ 0.4\%   &  significant \\

@@

\hline\hspace{0.5em} binary-trees:      & 1.019x as slow &   3.0ms $\pm$ 0.9\% &    3.0ms $\pm$ 0.9\%   &  significant \\
\hline\hspace{0.5em} fannkuch:          & 1.034x as fast   &   8.8ms $\pm$ 0.3\% &    8.5ms $\pm$ 0.4\%   &  significant \\
\hline\hspace{0.5em} nbody:             & 1.035x as fast   &   3.6ms $\pm$ 0.6\% &    3.5ms $\pm$ 0.3\%   &  significant \\
\hline\hspace{0.5em} nsieve:            & 1.052x as slow &   3.1ms $\pm$ 0.6\% &    3.3ms $\pm$ 0.5\%   &  significant \\

@@

\hline\hspace{0.5em} 3bit-bits-in-byte: & 1.009x as fast   &   1.0ms $\pm$ 0.6\% &    1.0ms $\pm$ 0.6\%   &  significant \\
\hline\hspace{0.5em} bits-in-byte:      & 1.023x as fast   &   4.1ms $\pm$ 0.5\% &    4.0ms $\pm$ 0.6\%   &  significant \\
\hline\hspace{0.5em} bitwise-and:       & ??               &   2.8ms $\pm$ 0.5\% &    2.8ms $\pm$ 0.6\%   &  \textit{might} be 1.005x as slow \\
\hline\hspace{0.5em} nsieve-bits:       & -                &   3.6ms $\pm$ 0.5\% &    3.6ms $\pm$ 0.5\% & \\

@@

\hline\hspace{0.5em} recursive:         & 1.020x as slow &   2.3ms $\pm$ 0.7\% &    2.3ms $\pm$ 0.4\%   &  significant \\

@@

\hline\hspace{0.5em} aes:               & 1.009x as slow &  15.5ms $\pm$ 0.4\% &   15.6ms $\pm$ 0.4\%   &  significant \\
\hline\hspace{0.5em} md5:               & ??               &   6.9ms $\pm$ 0.7\% &    6.9ms $\pm$ 0.4\%   &  \textit{might} be 1.006x as slow \\
\hline\hspace{0.5em} sha1:              & 1.008x as slow &   4.9ms $\pm$ 0.5\% &    4.9ms $\pm$ 0.5\%   &  significant \\

@@

\hline\hspace{0.5em} format-tofte:      & -                &  42.6ms $\pm$ 0.2\% &   42.6ms $\pm$ 0.2\%   & \\
\hline\hspace{0.5em} format-xparb:      & 1.023x as fast   &  20.0ms $\pm$ 0.3\% &   19.5ms $\pm$ 0.3\%   &  significant \\

@@

\hline\hspace{0.5em} cordic:            & 1.021x as fast   &   2.7ms $\pm$ 0.4\% &    2.6ms $\pm$ 0.6\%   &  significant \\
\hline\hspace{0.5em} partial-sums:      & -                &   7.1ms $\pm$ 0.5\% &    7.1ms $\pm$ 0.6\% & \\
\hline\hspace{0.5em} spectral-norm:     & 1.024x as slow &   3.4ms $\pm$ 0.6\% &    3.5ms $\pm$ 0.4\%   &  significant \\

@@

\hline\hspace{0.5em} dna:               & 1.012x as fast   &  10.2ms $\pm$ 0.5\% &   10.0ms $\pm$ 0.4\%   &  significant \\

@@

\hline\hspace{0.5em} base64:            & ??               &   4.9ms $\pm$ 0.6\% &    4.9ms $\pm$ 0.4\%   &  \textit{might} be 1.006x as slow \\
\hline\hspace{0.5em} fasta:             & 1.012x as slow &   6.9ms $\pm$ 0.5\% &    6.9ms $\pm$ 0.4\%   &  significant \\
\hline\hspace{0.5em} tagcloud:          & -                &  23.2ms $\pm$ 0.4\% &   23.3ms $\pm$ 0.3\% & \\
\hline\hspace{0.5em} unpack-code:       & 1.014x as slow &  39.5ms $\pm$ 0.2\% &   40.1ms $\pm$ 0.3\%   &  significant \\
\hline\hspace{0.5em} validate-input:    & 1.007x as slow &   6.8ms $\pm$ 0.4\% &    6.9ms $\pm$ 0.5\%   &  significant  \\

@@

\begin{figure}[H]
\begin{tabular}{|l|l|l|l|l|}
\hline
    \textbf{Test}     &\textbf{Comparison} & \textbf{From}        & \textbf{To}           &  \textbf{Details} \\
\hline\hline
    Total:                      & 1.015x as fast   & 2319.6ms $\pm$ 0.3\% &  2285.4ms $\pm$ 0.4\%  &   significant\\
\hline\hline
      ai:                       & 1.118x as fast   &  121.3ms $\pm$ 0.8\% &   108.5ms $\pm$ 1.2\%  &   significant\\
\hline\hspace{0.5em} astar:                  & 1.118x as fast   &  121.3ms $\pm$ 0.8\% &   108.5ms $\pm$ 1.2\%  &   significant\\
\hline\hline
      audio:                    & -                &  842.8ms $\pm$ 0.4\% &   838.0ms $\pm$ 0.7\%  &\\
\hline\hspace{0.5em} beat-detection:         & ??               &  393.0ms $\pm$ 1.0\% &   397.6ms $\pm$ 1.5\%  &   \textit{might} be 1.012x as slow\\
\hline\hspace{0.5em} dft:                    & 1.030x as fast   &  162.6ms $\pm$ 0.6\% &   157.8ms $\pm$ 0.5\%  &   significant\\
\hline\hspace{0.5em} fft:                    & 1.016x as fast   &  123.5ms $\pm$ 0.2\% &   121.6ms $\pm$ 0.4\%  &   significant\\
\hline\hspace{0.5em} oscillator:             & 1.017x as fast   &  163.7ms $\pm$ 0.3\% &   160.9ms $\pm$ 0.3\%  &   significant\\
\hline\hline
      imaging:                  & 1.020x as fast   &  569.1ms $\pm$ 0.9\% &   557.9ms $\pm$ 1.3\%  &   significant\\
\hline\hspace{0.5em} gaussian-blur:          & -                &  197.2ms $\pm$ 1.7\% &   193.7ms $\pm$ 2.1\%  &\\
\hline\hspace{0.5em} darkroom:               & -                &  248.2ms $\pm$ 0.3\% &   247.6ms $\pm$ 0.4\%  &\\
\hline\hspace{0.5em} desaturate:             & 1.062x as fast   &  123.8ms $\pm$ 3.2\% &   116.7ms $\pm$ 5.1\%  &   significant\\
\hline\hline
      json:                     & 1.019x as fast   &  121.3ms $\pm$ 0.2\% &   119.0ms $\pm$ 0.4\%  &   significant\\
\hline\hspace{0.5em} parse-financial:        & 1.005x as fast   &   75.8ms $\pm$ 0.2\% &    75.5ms $\pm$ 0.4\%  &   significant\\
\hline\hspace{0.5em} stringify-tinderbox:    & 1.044x as fast   &   45.5ms $\pm$ 0.5\% &    43.5ms $\pm$ 0.8\%  &   significant\\
\hline\hline
      stanford:                 & -                &  665.0ms $\pm$ 0.5\% &   662.2ms $\pm$ 0.4\%  &\\
\hline\hspace{0.5em} crypto-aes:             & -                &  160.7ms $\pm$ 1.5\% &   160.6ms $\pm$ 1.1\%  &\\
\hline\hspace{0.5em} crypto-ccm:             & 1.008x as slow &  158.6ms $\pm$ 0.4\% &   159.8ms $\pm$ 0.5\%  &   significant\\
\hline\hspace{0.5em} crypto-pbkdf2:          & 1.006x as fast   &  254.9ms $\pm$ 0.5\% &   253.3ms $\pm$ 0.4\%  &   significant\\
\hline\hspace{0.5em} crypto-sha256-iterative:& 1.025x as fast   &   90.8ms $\pm$ 0.4\% &    88.5ms $\pm$ 0.5\%  &   significant \\
\hline
\end{tabular}
\caption{Kraken benchmark results}
\label{fig:kraken}
\end{figure}
